### 2019-02-17 manuscript/results.tex
latex code for supplemental figures
updated main figures
- starting paragraph minor comments/changes.
many comments, while talking with Boris
outline for Intro
table skeleton for median rate estimates
initial thoughts for Discussion
notes to include pathways ala robertson2011
misc elsewhere

@@

>>>>

% E & B:  We just spent awhile poring over the great supp figures of rate estimates, which are essential to grasp the uncertainties.  But to facilitate quick comparisons across models, could we have a table of the median rate estimates for all models?  Possibly like the format I've laid out below?  Or maybe there's a better way.

\begin{supptable}
    \begin{center}
    \begin{tabular}{lcccccc}
                       & D/P & D/P+A/B & I/C & I/C+A/B & ID/CD/CP & ID/CD/CP+A/B \\ \midrule
        %
        $r_D$          &     &         & --- & ---     & ---      & ---          \\
        $r_P$          &     &         & --- & ---     & ---      & ---          \\
        $r_I$          & --- & ---     &     &         & ---      & ---          \\
        $r_C$          & --- & ---     &     &         & ---      & ---          \\
        $r_{ID}$       & --- & ---     & --- & ---     &          &              \\
        $r_{CD}$       & --- & ---     & --- & ---     &          &              \\
        $r_{CP}$       & --- & ---     & --- & ---     &          &              \\
        %
        $\rho$         &     &         & --- & ---     & ---      & ---          \\
        $\rho_I$       & --- & ---     & --- & ---     &          &              \\
        $\rho_C$       & --- & ---     & --- & ---     &          &              \\
        $\delta$       &     &         &     &         &          &              \\
        $q_{IC}$       & --- & ---     &     &         &          &              
    \end{tabular}

    \vspace{12pt}
    \begin{tabular}{lcccccc}
                       & D/P & D/P+A/B & I/C & I/C+A/B & ID/CD/CP & ID/CD/CP+A/B \\ \midrule
        %
        $r_D$          &     &         & --- & ---     & ---      & ---          \\
        $r_P$          &     &         & --- & ---     & ---      & ---          \\
        $r_I$          & --- & ---     &     &         & ---      & ---          \\
        $r_C$          & --- & ---     &     &         & ---      & ---          \\
        $r_{ID}$       & --- & ---     & --- & ---     &          &              \\
        $r_{CD}$       & --- & ---     & --- & ---     &          &              \\
        $r_{CP}$       & --- & ---     & --- & ---     &          &              \\
        %
        $\rho$         &     &         & --- & ---     & ---      & ---          \\
        $\rho_I$       & --- & ---     & --- & ---     &          &              \\
        $\rho_C$       & --- & ---     & --- & ---     &          &              \\
        $q_{IC}$       & --- & ---     &     &         &          &              
    \end{tabular}
    \end{center}
    \caption{median rate estimates for all models (see supp figs for more details and uncertainties); when there are two numbers in one cell, they're for the A and B hidden states; --- means that parameter was not present in the model; upper section is for models with $\delta$ and lower section is for models without}
    \label{table:estimates}
\end{supptable}

@@

\begin{figure}
\includegraphics[width=\textwidth]{netdiversificationallnodip.pdf}
  \caption{Net diversification rates for all models that do not include diploidization.}  
\label{figure:netdivnodip}
\end{figure}

\begin{suppfigure}
\includegraphics[width=\textwidth]{bisseDPposteriordist.pdf}
\caption{Posterior distribution for each of the parameters in the D/P polyploidy model} % XXX
\label{suppfigure:DP}
\end{suppfigure}

\begin{suppfigure}
\includegraphics[width=\textwidth]{bisseDPnodipposteriordist.pdf}
\caption{Posterior distribution for each of the parameters in the D/P no $\delta$ polyploidy model} % XXX
\label{suppfigure:DPnodip}
\end{suppfigure}

\begin{suppfigure}
\includegraphics[width=\textwidth]{hisseDPposteriordist.pdf}
\caption{Posterior distribution for each of the parameters in the D/P-A/B polyploidy model} % XXX
% fixme: offset plotting error in "relative extinction" panel
\label{suppfigure:DPAB}
\end{suppfigure}

\begin{suppfigure}
\includegraphics[width=\textwidth]{hisseDPnodipposteriordist.pdf}
\caption{Posterior distribution for each of the parameters in the D/P no $\delta$-A/B polyploidy model} % XXX
\label{suppfigure:DPnodipAB}
\end{suppfigure}

\begin{suppfigure}
\includegraphics[width=\textwidth]{bisseSIposteriordist.pdf}
\caption{Posterior distribution for each of the parameters in the I/C breeding system model} % XXX
\label{suppfigure:IC}
\end{suppfigure}

\begin{suppfigure}
\includegraphics[width=\textwidth]{hisseSInoretposteriordist.pdf}
\caption{Posterior distribution for each of the parameters in the I/C-A/B breeding system model} % XXX
\label{suppfigure:ICAB}
\end{suppfigure}

\begin{suppfigure}
\includegraphics[width=\textwidth]{musseDPSIposteriordist.pdf}
\caption{Posterior distribution for each of the parameters in the ID/CD/CP polyploidy and breeding system model} % XXX
\label{suppfigure:IDCDCP}
\end{suppfigure}

\begin{suppfigure}
\includegraphics[width=\textwidth]{musseDPSInodipposteriordist.pdf}
\caption{Posterior distribution for each of the parameters in the ID/CD/CP no $\delta$ polyploidy and breeding system model} % XXX
\label{suppfigure:IDCDCPnodip}
\end{suppfigure}

\begin{suppfigure}
\includegraphics[width=\textwidth]{muhisseDPSIposteriordist.pdf}
\caption{Posterior distribution for each of the parameters in the ID/CD/CP-A/B polyploidy and breeding system model} % XXX
\label{suppfigure:IDCDCPAB}
\end{suppfigure}

\begin{suppfigure}
\includegraphics[width=\textwidth]{muhisseDPSInodipposteriordist.pdf}
\caption{Posterior distribution for each of the parameters in the ID/CD/CP no $\delta$- A/B polyploidy and breeding system model} % XXX
\label{suppfigure:IDCDCPnodipAB}
\end{suppfigure}

% E or R todo: which pathway from SI-D to SC-P is more common, based on rate estimates?  apply procedure from robertson2011 to rates from ID/CD/CP model
